A lottery model of density-dependent selection

### 2017-10-11 manuscript.tex
latest

%\textit{Manuscript type}: Article. 
% Or e-article, note, e-note, natural history miscellany,
% e-natural history miscellany, comment, reply, symposium, or
% countdown to 150.

%\noindent{\footnotesize Prepared using the suggested \LaTeX{} 
%template for \textit{Am.\ Nat.}}

@@

@@

Yet selection does not only change relative genotypic proportions. Ultimately, it involves the births and deaths of individuals, and is therefore intimately connected to changes in absolute abundance \cite{evolution_demography_stuff}. This immediately poses a challenge: any description of evolution grounded in abundances needs to specify how population density is regulated, as well as how fitness depends on density, which may differ between genotypes (density-dependent selection). As a result, the early density-dependent selection literature was among the first to explicitly grapple with the interplay between ecology and evolution \citep{travis_2013}.

Much of the work on density-dependent selection grew out of MacArthur's $r$/$K$-selection scheme \citep{macarthur_1962,macarthur_1967} in which $r$-selection favors faster growth at low density, whereas $K$-selection favors the ability to keep growing at high density. Although $r$ and $K$ are named after the common ``carrying capacity'' parameterization of the logistic model, the concepts of $r$- and $K$-selection are not restricted to that model \citep{macarthur_1967}. Nevertheless, much of the density-dependent selection literature has adopted variants of the logistic model, often in the setting of Mendelian inheritance \cite{roughgarden etc}.

>>>>

@@

Some of the earliest explicit discussions of the interplay between ecology and evolution appear in the density-dependent selection literature \citep{travis_2013}.

Much of this work grew out of MacArthur's $r$/$K$-selection scheme \citep{macarthur_1962,macarthur_1967} in which $r$-selection favors faster growth at low density, whereas $K$-selection favors the ability to keep growing at high density.

Although $r$ and $K$ are named after the common ``carrying capacity'' parameterization of the logistic model, the concepts of $r$- and $K$-selection are not restricted to that model \citep{macarthur_1967}.

Yet selection does not only change relative genotypic proportions. Ultimately, it involves the births and deaths of individuals, and is therefore intimately connected to changes in absolute abundance \cite{evolution_demography_stuff}. This immediately poses a challenge: any description of evolution grounded in abundances needs to specify how population density is regulated, as well as how fitness depends on density, which may differ between genotypes (density-dependent selection). As a result,

@@

 Nevertheless, much of the density-dependent selection literature has adopted variants of the logistic model, often in the setting of Mendelian inheritance \cite{roughgarden etc}.
